Supplemental Materials, Methods and Results

### 2022-02-24 supp/Supplemental Materials and Methods.Rmd
Cleaning up a bit of unecessary code

     #gs <- gs_title("q10_newdata")
    #data <- as_tibble(gs_read(ss = gs))

@@

    #data <- read_sheet(ss = "q10_newdata")
    data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
    data$lat <- as.numeric(data$lat)
    new_papers <- data[-grep("_o", data$record_num),]
    old_papers <- data[grep("_o", data$record_num),]

>>>>

@@

          data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
      data$lat <- as.numeric(data$lat)
    new_papers <- data[-grep("_o", data$record_num),]
    old_papers <- data[grep("_o", data$record_num),]
